Towards a universal-dependency treebank for Kazakh

### 2015-06-17 2015-turklang-kazdep/paper.tex
stuffs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60802 72bbbca6-d526-0410-a7d9-f06f51895060

\title{Dependency Treebank for Kazakh based on Universal Dependencies}
\name{Francis Tyers$^a$ and Jonathan Washington$^b$}
\address{$^a$ hargle,\\
	$^b$ Departments of Linguistics and Central Eurasian Studies, Indiana University, Bloomington, IN 47405, USA}

@@

\subsection{The Kazakh Language}

@@

>>>>

\title{Towards a universal-dependency treebank for Kazakh}
\name{Francis M. Tyers$^\dagger$ and Jonathan Washington$^\ast$}
\address{$^\dagger$ HSL-fakultehta, UiT Norgga árktalaš universitehta, N-9015 Tromsø, Norway\\
	$^\ast$ Departments of Linguistics and Central Eurasian Studies, Indiana University, Bloomington, IN 47405, USA}

@@

\subsection{Kazakh}

@@

\section*{Acknowledgements}
